word-cloud

### 2016-08-03 eda/business-attributes.Rmd
cleaning data

```{r}
us_business <- read_csv('../clean_data/us-business.csv', stringsAsFactors=FALSE)
noise_level <- read_csv('../clean_data/noise-attr.csv', stringsAsFactors=FALSE) 
attire_type <- read_csv('../clean_dta/attire-attr.csv', stringsAsFactors=FALSE)
states <- map_data('state')
ggplot(states) + 
  geom_polygon(aes(x = long, 
                   y = lat, 
                   group = group), 
               fill = "grey80", 
               color = "white") + 
  coord_fixed(1.3) + 
  geom_point(data = us_business, 
             aes(long, 
                 lat, 
                 color = factor(stars), 
                 size = count), 
             alpha = 0.7) + 
  guides(colour = guide_legend("Star Rating"), 
         size = guide_legend("Review Counts")) + 
  labs(title = "Restaurant Reviews in United States") +
  theme_nothing(legend = TRUE)
```

>>>>

```{r}
us_business <- read_csv('../clean_data/us-business.csv')
noise_level <- read_csv('../clean_data/noise-attr.csv')
attire_type <- read_csv('../clean_data/attire-attr.csv')
states <- map_data('state')
ggplot(states) + 
  geom_polygon(aes(x = long, 
                   y = lat, 
                   group = group), 
               fill = "grey80", 
               color = "white") + 
  coord_fixed(1.3) + 
  geom_point(data = us_business, 
             aes(long, 
                 lat, 
                 color = factor(stars), 
                 size = count), 
             alpha = 0.7) + 
  guides(colour = guide_legend("Star Rating"), 
         size = guide_legend("Review Counts")) + 
  labs(title = "Restaurant Reviews in United States") +
  theme_nothing(legend = TRUE)
```

### 2016-08-03 eda/word-cloud.Rmd
cleaning data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(wordcloud)
library(readr)
library(dplyr)
library(tidyr)
```

@@

col <- c("salmon1", "tomato2", "orangered3", "red3", "firebrick4")
wordcloud(one$word, one$n, scale = c(4, 0.25),
          random.order = F, random.color = F,
          use.r.layout = T, rot.per = .35,
          colors = col)
green <- c("chartreuse2", "mediumseagreen", "forestgreen", 
           "seagreen", "darkgreen")
wordcloud(five$word, five$n, scale = c(4, 0.25),
          random.order = F, random.color = F,
          use.r.layout = T, rot.per = .35,
          colors = green)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(wordcloud)
library(readr)
library(dplyr)
library(tidyr)
source("../functions/wordcloud.R")
```

@@

red <- c("salmon1", "tomato2", "orangered3", "red3", "firebrick4")
word_cloud(one$word, one$n, red)
green <- c("chartreuse2", "mediumseagreen", "forestgreen", 
           "seagreen", "darkgreen")
word_cloud(five$word, five$n, green)
```
